\section*{Executive Summary}
\label{chap:exSummary}

This report showcases the company MjøsTaxis expansion into two new locations, and upgrade to a digitalized system.
The company needs infrastructure to handle a whole new digital system allowing for fare-orders through a web-app and better information flow between employees and their respective departments.

The report includes a detailed suggestion on implementing a security policy that will reduce the chances of Mjøstaxi being the victim of malicious activity.
The security policy recommends introducing security education to the employees based on their role and privileges within the company.
There are also recommendations as to how user passwords should be made and handled, along with introducing password managers to promote having better and more secure passwords.
Every device owned and used by Mjøstaxi must have some kind of authentication, at least a password if not more.
Backup routines must also be put in place to prevent loss of data.
The policy also covers what will happen to those who break it.

A modern business faces many potential risks in the cyber domain.
This report covers in detail what types of attacks are feasible, their likelihood, the consequences they can bring and suggestions to mitigate them.
There is also included a risk assessment matrix to help visualize the risks and the effect of the mitigations.

Further the design part of this report covers the different requirements set by Mjøstaxi's operations, how they are calculated and how they are addressed.

Securing the operations is also important. 
That is why this report suggests and facilitates multiple measurements to keep Mjøstaxi's operating securely and reduces potential liability.
Continuous delivery is important and therefore we also lay out a suggestion on moving some of the IT infrastructure to a cloud service provider instead.

All these requirements and solutions introduce a lot of different technologies that are described in chapter \ref{chap:technology}.

Finally we describe the suggested topology that should cover all of Mjøstaxi's communication, redundancy and security needs. 



